\documentclass[12pt,a4paper,austrian]{article}
\usepackage{graphicx}
\usepackage[austrian, english]{babel}
\usepackage[utf8]{inputenc}
%\usepackage{listings}
\usepackage{multirow}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb} % fuer Mengen \N, Q, C, R
\graphicspath{{./fig/}}


%% Satzspiegel
\setlength{\hoffset}{-1in} \setlength{\textwidth}{18cm}
\setlength{\oddsidemargin}{1.5cm}
\setlength{\evensidemargin}{1.5cm}
\setlength{\marginparsep}{0.7em}
\setlength{\marginparwidth}{0.5cm}

\setlength{\voffset}{-1.9in}
\setlength{\headheight}{12pt}
\setlength{\topmargin}{2.6cm}
   \addtolength{\topmargin}{-\headheight}
\setlength{\headsep}{3.5cm}
   \addtolength{\headsep}{-\topmargin}
   \addtolength{\headsep}{-\headheight}
\setlength{\textheight}{27cm}

%% How should floats be treated?
\setlength{\floatsep}{12 pt plus 0 pt minus 8 pt}
\setlength{\textfloatsep}{12 pt plus 0pt minus 8 pt}
\setlength{\intextsep}{12 pt plus 0pt minus 8 pt}

\tolerance2000
\emergencystretch20pt

%% Text appearence
% English text
\newcommand{\eg}[1]%
  {\selectlanguage{english}\textit{#1}\selectlanguage{austrian}}

\newcommand{\filename}[1]
  {\begin{small}\texttt{#1}\end{small}}

\newcommand\IFT{\unitlength1mm\begin{picture}(10,2) \put (1,1)
{\circle{1.7}} \put(2,1){\line(1,0){5}} \put(8,1)
{\circle*{1.7}}\end{picture}}
\newcommand\FT{\unitlength1mm\begin{picture}(10,2) \put (1,1)
{\circle*{1.7}} \put(2,1){\line(1,0){5}} \put(8,1)
{\circle{1.7}}\end{picture}}

% A box for multiple choice problems
\newcommand{\choicebox}{\fbox{\rule{0pt}{0.5ex}\rule{0.5ex}{0pt}}}

\newenvironment{wahrfalsch}%
  {\bigskip\par\noindent\makebox[1cm][c]{richtig}\hspace{3mm}\makebox[1cm][c]{falsch}
   \begin{list}%
   {\makebox[1cm][c]{\choicebox}\hspace{3mm}\makebox[1cm][c]{\choicebox}}%
   {\setlength{\labelwidth}{2.31 cm}\setlength{\labelsep}{3mm}
    \setlength{\leftmargin}{2.61 cm}\setlength{\listparindent}{0pt}
    \setlength{\itemindent}{0pt}}%
  }
  {\end{list}}

\newcounter{theaufgabe}\setcounter{theaufgabe}{1}
\newenvironment{aufgabe}[1]%
  {\bigskip\par\noindent\begin{nopagebreak}
   \textsf{\textbf{\arabic{theaufgabe}.\thinspace Aufgabe}}\quad
      \textsf{\textit{#1}}\\*[1ex]%
\stepcounter{theaufgabe}\hspace{2ex}\end{nopagebreak}}
  {\par\pagebreak[2]}

% Innerhalb der Aufgaben erfolgt die weitere Unterteilung mittels einer
% enumerate Umgebung, die allerdings a), b),... zaehlen soll.
\renewcommand{\labelenumi}{\alph{enumi})}
\renewcommand{\labelenumii}{\arabic{enumii})}

% A box to tick for everything which has to done
\newcommand{\abgabe}{\marginpar{$\Box$}}
% Margin paragraphs on the left side
\reversemarginpar

% Language for listings
%\lstset{language=Vhdl,
%  basicstyle=\small\tt,
 % keywordstyle=\tt\bf,
 % commentstyle=\sl}

% No indention
\setlength{\parindent}{0.0cm}
% Don't number sections
\setcounter{secnumdepth}{0}


%% Beginning of the text

\begin{document}
\selectlanguage{austrian}
\pagestyle{plain}


%===  This is the header section ============================================================
\thispagestyle{empty}
\noindent
\begin{minipage}[b][4cm]{1.0\textwidth}  
\begin{center}
\begin{bf} 
\begin{large} Digital Signal Processing SS 2024 -- 3.~Assignment\end{large} \\
\vspace{0.3cm}
\begin{Large} Sampling and Reconstruction \end{Large} \\
\vspace{0.3cm}
\end{bf}
\begin{large}
Group 22\\
Julian Feichtinger, K12015812\\
Wolfram Laube, K08900915\\
\end{large} 
\end{center}
\end{minipage}

\noindent \rule[0.8em]{\textwidth}{0.12mm}\\[-0.5em]
%=======================================================================================


\begin{aufgabe}{Sampling $1(40 \%)$}

The analogue signal

\[
x(t) = x_{1}(t) + x_{2}(t) = \sin \left(2 \pi f_{1} t\right) + \sin \left(2 \pi f_{2} t\right)
\]

with \(f_{1} = 4 \mathrm{kHz}\) and \(f_{2} = 6 \mathrm{kHz}\) is sampled with a sampling rate of \(f_{s} = 10 \mathrm{kHz}\) to yield the discrete time signal \(x[n]\).

\begin{enumerate}[label=\alph*)]
    \item Draw the spectrum of \(x(t)\).

    \item Due to sampling frequency shifted versions of the analogue spectrum are generated.

    Draw the spectra shifted by \(-f_{s}, 0\) and \(+f_{s}\) and then the spectrum for \(x[n]\) as a result of spectral addition in one diagram.
    The diagram should show the spectra in the range from \(-f_{s}\) to \(+f_{s}\).

    \emph{Hint: Draw real and imaginary parts of the spectrum rather than magnitude and phase to ease addition.}

    \item In Matlab, plot the section 0 to \(2 \mathrm{~ms}\) of the signal \(x(t)\) with a sampling rate of \(100 \mathrm{kHz}\) to emulate an analogue signal.

    Then also add the sampled signal \(x[n] = x\left(n T_{s}\right)\) to the same plot.
    Show that \(x[n]\) corresponds to the spectrum derived in (b).
\end{enumerate}


\hrule
\begin{enumerate}
%\input{ex1_a_python_wip_wolfram}
%\input{ex1_b_wip_wolfram}
%\input{ex1_c_wip_wolfram}
%\input{ex1_d_python_wip_wolfram}
%\input{ex1_e_python_wip_wolfram}
%\input{ex1_f_python_wip_wolfram}
\end{enumerate}

\end{aufgabe}

\begin{aufgabe}{Convolution-1 (20\%)}

The signal $x[n]=(3,-1,2,0,1)$ at sample times $n=(0,1,2,3,4)$ is the input to an LTI system with impulse response $h[n]=(2,3,4,1)$ at sample times $n=(0,1,2,3)$.

\begin{enumerate}
\item[(a)]
How long is the output signal $y[n]$?
\item[(b)]
Manually calculate the output signal $y[n]$.
\end{enumerate}
\hrule

\begin{enumerate}
%\input{ex2_a_wip_wolfram}
%\input{ex2_b_wip_wolfram}
\end{enumerate}

\end{aufgabe}

\begin{aufgabe}{Convolution-2 (25\%)}

Consider a Linear Time-Invariant (LTI) system with an impulse response
given by $h[n] = (0.25, 0.5, 0.25)$ at sample indices $n = (0, 1, 2)$.

The input signal is defined as $x[n] = \cos \left(\frac{2 \pi}{20} n\right)$ for $0 \leq n < 50$.

\begin{enumerate}
\item[(a)]
What is the length $L_y$ of the output signal $y[n]$?

\item[(b)]
Implement the convolution operation $y[n] = \sum_{i=0}^{L_{h}-1} h[i] x[n-i]$ in Matlab using two nested for-loops.
The outer for-loop should increment the output index $n$, and the inner for-loop should increment the memory index $i$.
Calculate all $L_y$ output samples of $y[n]$.

\item[(c)]
Plot the signal $y[n]$.

\item[(d)]
Verify the correct implementation of the convolution using the Matlab function \texttt{conv}.
Plot both signals on top of each other, with the directly calculated signal in a solid line style
and the signal obtained via \texttt{conv} in a dashed style.
Provide a legend for your plot.

\end{enumerate}
\hrule

\begin{enumerate}
%\input{ex3_a_wip_wolfram}
%\input{ex3_b_python_wip_wolfram}
%\input{ex3_c_python_wip_wolfram}
%\input{ex3_d_python_wip_wolfram}
\end{enumerate}

\end{aufgabe}

\begin{aufgabe}{Discrete Time Fourier Transform (25\%)}
The time discrete sequence $x[n]=(0.8)^{|n|}(u[n+10]-u[n-11])$ should be transformed to the frequency domain
by using the discrete time Fourier transform (DTFT).
As $x[n]$ has finite support (that means it is a sequence of finite length), $X\left(e^{j \Omega}\right)$
can be determined numerically via Matlab (or alternatively Octave, Python).

\begin{enumerate}
\item[(a)]
Create a Matlab function, that is able to calculate the DTFT of a finite sequence.
The function should provide the following interface:

% Interface is described in the attached screenshot.

Try to avoid for loops!
You are still allowed to use for loops, however there will be a small deduction in points for the case you need to use for loops.

\item[(b)]
Plot magnitude and phase response of $X\left(e^{j \Omega}\right)$ for the interval $-\pi \leq \Omega \leq \pi$
within single subplots.
What do you observe for the phase response (hint: you should have a close look at the scaling of the $y$ axis)?

\item[(c)]
Vary the parameter $\Omega$.
What do you observe in the spectrum?
\end{enumerate}

\hrule

\begin{enumerate}
%\input{ex4_a_python_wip_wolfram}
%\input{ex4_b_python_wip_wolfram}
%\input{ex4_c_python_wip_wolfram}
\end{enumerate}

\end{aufgabe}


\end{document}
