\documentclass[12pt,a4paper,austrian]{article}
\usepackage{graphicx}
\usepackage[austrian, english]{babel}
\usepackage[utf8]{inputenc}
%\usepackage{listings}
\usepackage{multirow}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb} % fuer Mengen \N, Q, C, R
\graphicspath{{./fig/}}


%% Satzspiegel
\setlength{\hoffset}{-1in} \setlength{\textwidth}{18cm}
\setlength{\oddsidemargin}{1.5cm}
\setlength{\evensidemargin}{1.5cm}
\setlength{\marginparsep}{0.7em}
\setlength{\marginparwidth}{0.5cm}

\setlength{\voffset}{-1.9in}
\setlength{\headheight}{12pt}
\setlength{\topmargin}{2.6cm}
   \addtolength{\topmargin}{-\headheight}
\setlength{\headsep}{3.5cm}
   \addtolength{\headsep}{-\topmargin}
   \addtolength{\headsep}{-\headheight}
\setlength{\textheight}{27cm}

%% How should floats be treated?
\setlength{\floatsep}{12 pt plus 0 pt minus 8 pt}
\setlength{\textfloatsep}{12 pt plus 0pt minus 8 pt}
\setlength{\intextsep}{12 pt plus 0pt minus 8 pt}

\tolerance2000
\emergencystretch20pt

%% Text appearence
% English text
\newcommand{\eg}[1]%
  {\selectlanguage{english}\textit{#1}\selectlanguage{austrian}}

\newcommand{\filename}[1]
  {\begin{small}\texttt{#1}\end{small}}

\newcommand\IFT{\unitlength1mm\begin{picture}(10,2) \put (1,1)
{\circle{1.7}} \put(2,1){\line(1,0){5}} \put(8,1)
{\circle*{1.7}}\end{picture}}
\newcommand\FT{\unitlength1mm\begin{picture}(10,2) \put (1,1)
{\circle*{1.7}} \put(2,1){\line(1,0){5}} \put(8,1)
{\circle{1.7}}\end{picture}}

% A box for multiple choice problems
\newcommand{\choicebox}{\fbox{\rule{0pt}{0.5ex}\rule{0.5ex}{0pt}}}

\newenvironment{wahrfalsch}%
  {\bigskip\par\noindent\makebox[1cm][c]{richtig}\hspace{3mm}\makebox[1cm][c]{falsch}
   \begin{list}%
   {\makebox[1cm][c]{\choicebox}\hspace{3mm}\makebox[1cm][c]{\choicebox}}%
   {\setlength{\labelwidth}{2.31 cm}\setlength{\labelsep}{3mm}
    \setlength{\leftmargin}{2.61 cm}\setlength{\listparindent}{0pt}
    \setlength{\itemindent}{0pt}}%
  }
  {\end{list}}

\newcounter{theaufgabe}\setcounter{theaufgabe}{1}
\newenvironment{aufgabe}[1]%
  {\bigskip\par\noindent\begin{nopagebreak}
   \textsf{\textbf{\arabic{theaufgabe}.\thinspace Aufgabe}}\quad
      \textsf{\textit{#1}}\\*[1ex]%
\stepcounter{theaufgabe}\hspace{2ex}\end{nopagebreak}}
  {\par\pagebreak[2]}

% Innerhalb der Aufgaben erfolgt die weitere Unterteilung mittels einer
% enumerate Umgebung, die allerdings a), b),... zaehlen soll.
\renewcommand{\labelenumi}{\alph{enumi})}
\renewcommand{\labelenumii}{\arabic{enumii})}

% A box to tick for everything which has to done
\newcommand{\abgabe}{\marginpar{$\Box$}}
% Margin paragraphs on the left side
\reversemarginpar

% Language for listings
%\lstset{language=Vhdl,
%  basicstyle=\small\tt,
 % keywordstyle=\tt\bf,
 % commentstyle=\sl}

% No indention
\setlength{\parindent}{0.0cm}
% Don't number sections
\setcounter{secnumdepth}{0}


%% Beginning of the text

\begin{document}
\selectlanguage{austrian}
\pagestyle{plain}


%===  This is the header section ============================================================
\thispagestyle{empty}
\noindent
\begin{minipage}[b][4cm]{1.0\textwidth}  
\begin{center}
\begin{bf} 
\begin{large} Digital Signal Processing SS 2024 -- 1.~Assignment\end{large} \\
\vspace{0.3cm}
\begin{Large} Analogue Signals and Systems  \end{Large} \\
\vspace{0.3cm}
\end{bf}
\begin{large}
Group 22\\
Julian Feichtinger, K12015812\\
Wolfram Laube, K08900915\\
\end{large} 
\end{center}
\end{minipage}

\noindent \rule[0.8em]{\textwidth}{0.12mm}\\[-0.5em]
%=======================================================================================


\begin{aufgabe}{Complex Numbers (20\%)}
These complex numbers are given:

$$
\begin{aligned}
& c_{1}=-5+j 3 \\
& c_{2}=\frac{\sqrt{2}}{2} e^{-\frac{j 3 \pi}{4}} \\
& c_{3}=\frac{1}{\sqrt{2}}+\frac{j 1}{\sqrt{2}}
\end{aligned}
$$

Calculate the following numbers and show the calculations/derivations in the report.

$$
\begin{aligned}
& c_{4}=c_{1}+c_{2} \\
& c_{5}=c_{1} \cdot c_{2} \\
& c_{6}=\left|c_{3}\right|^{2} \\
& c_{7}=\arg \left(c_{3}\right) \\
& c_{8}=\frac{c_{1}}{c_{2}} \\
& c_{9}=c_{1} \cdot c_{1}^{*}
\end{aligned}
$$

Subsequently check your results with Matlab. Useful functions in this context are abs and angle.
You do not need to add those checks to your report, or show the corresponding code.

\hrule

\input{ex1_wip_wolfram.tex}

\end{aufgabe}

\begin{aufgabe}{Fourier Transform (25\%)}
The lecture notes show the following Fourier transform pair for the cosine wave (DSP\_2.pdf, page 37):

$$
x(t)=\hat{X} \cos \left(2 \pi f_{0} t\right) \leftrightarrow X(f)=\frac{\hat{X}}{2} \delta\left(f-f_{0}\right)+\frac{\hat{X}}{2} \delta\left(f+f_{0}\right)
$$

\begin{enumerate}
\item[a)]
Mathematically proof this relation. To do so, use Eulers formula to express the cosine in the
time domain as a sum of complex exponentials and the Fourier transform of a complex exponential function
from DSP\_2.pdf, page 38.

\item[b)]
Add a diagram of $X(f)$ in the report (draw the real and the imaginary part of $X(f)$ in the same diagram).
\end{enumerate}

\hrule

\begin{enumerate}
\input{ex2_a_wip_wolfram.tex}
\input{ex2_b_wip_wolfram.tex}
\end{enumerate}

\end{aufgabe}

\begin{aufgabe}{Time Shift and Phase (20\%)}
Given are two sines according to the following formula with $f_{1}=1 \mathrm{~Hz}$ and $f_{2}=3 \mathrm{~Hz}$.

$$
x_{i}(t)=\sin \left(2 \pi f_{i} t\right), \text { with } i \in\{1,2\}
$$

All two sines are time delayed by $\tau=0.1 \mathrm{~s}$ to yield

$$
y_{i}(t)=\sin \left(2 \pi f_{i}(t-0.1)\right) \text {. }
$$

This corresponds to a phase shift. Thus, the delayed sines may also be written as

$$
y_{i}(t)=\sin \left(2 \pi f_{i} t+\phi_{i}\right) .
$$

\begin{enumerate}
\item[a)] Calculate the phase shifts $\phi_{i}$ for each sine, and verify that this corresponds to the 'Shift Theorem' of the
Fourier Transform (DSP\_2.pdf, page 41).

\item[b)] For both sines in separated plots: Plot the original signal, the time delayed signal and the phase shifted signal.
Since the latter two are identical, show this by plotting the first with a solid line and the overlaid one in a
different colour with a dashed line. Plot each signal from 0 to $1 \mathrm{~s}$.
In Matlab use the following time-vector: $\mathrm{t}=0: 0.001: 1$.
\end{enumerate}

\hrule

\begin{enumerate}
\input{ex3_a_wip_wolfram.tex}
\input{ex3_b_wip_wolfram.tex}
\end{enumerate}

\end{aufgabe}

\begin{aufgabe}{Linearity and Time Invariance (35\%)}
Examine the following systems (input $x(t)$ and output $y(t)$ ) for linearity and time invariance.

Clearly show the mathematical derivations and state if the systems are linear and/or time-invariant.

\begin{enumerate}
\item[a)] $y(t)=(x(t))^{2}$
\item[b)] $y(t)=x(t) \cdot \sin \left(\Omega_{0} t\right)$
\end{enumerate}

\hrule

\begin{enumerate}
\input{ex4_a_wip_wolfram.tex}
\input{ex4_b_wip_wolfram.tex}
\end{enumerate}

\end{aufgabe}


\end{document}
